\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
strange format

@@

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmax_{\boldsymbol{\theta}} 
        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
        \lambda \text{Var}\left(\hat{V}(S_T;\boldsymbol{\theta})\right)
\end{equation}

where $\lambda$ represents risk aversion parameter.

>>>>

\input{method_comparison.tex}

The empirical results presented in Table~\ref{tab:method_comparison} demonstrate clear 
superiority of the weighted error method across all regularization parameters. While the 
L2 regularization provides an analytical solution, making it computationally attractive, 
the weighted method consistently achieves MAE around 1.04, significantly outperforming 
both L1 and L2 approaches. The L2 method shows stable but inferior performance with MAE 
around 1.45, while L1 regularization's performance deteriorates significantly as $\gamma$ 
increases, with MAE growing from 1.45 to 4.62.

This comprehensive comparison suggests that for practical applications, the weighted error 
method should be preferred despite its requirement for numerical optimization. The improved 
accuracy (approximately 30\% reduction in MAE compared to L2) and consistent performance 
across different regularization parameters justify the additional computational cost. 
Furthermore, the weighted method's focus on economically significant regions makes it 
particularly well-suited for real-world trading applications.

@@

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmax_{\boldsymbol{\theta}} 
        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
\end{equation}
